\documentclass[notitlepage]{report}
\usepackage[utf8]{inputenc}
\usepackage[top=6em, bottom=6em, left=1.2in, right=1.2in]{geometry}
\usepackage{ragged2e}
\date{\parbox{\linewidth}{\centering%
Sarangi Poornasri, 19120077\endgraf
Metallurgical and materials Engg 2021-22 (II) \endgraf
National Institute of Technology, Raipur\endgraf
\begin{flushright}
Guided By:-\endgraf
Dr.Saurabh Gupta\endgraf 
\end{flushright}}}
\begin{document}

\title{\textbf{\line(1,0){425}\\IMPACT OF CLOUD TECHNOLOGY ON ENTREPRENEURSHIP
\\\line(1,0){425}}}

\maketitle
\hrule{}


\section*{Introduction}

The cloud itself is simply a major component to define the internet. It can be used for networking and can also be used to host server of internet. All that’s needed to run cloud-based software is the computer itself and the network computers, servers, and data storage systems take care of the rest.

Since cloud has made it super easy to host the server and run, it’s gaining popularity both in small and large businesses, as it eliminates the data storage and memory consumption, by doing all the heavy lifting by itself.

Cloud computing is present everywhere and is used by every person in some or the other way unknowingly. The 2 cloud is used by the services which are web- based and provide e-mail or storage. As the technology is evolving at a tremendous rate and so are businesses are growing to match the technological advancements, the adoption of cloud computing is also increasing.

\section*{Cloud computing on startups}

The historical data of past three years points that in Greece the use of cloud computing has skyrocketed, companies are shifting from inhouse servers to cloud based servers as it comes with lots of cost benefits. Cloud technology is also acting like catalyst to instigate the boom of startup in Greece, since startups couldn’t afford inhouse servers, this is facilitating more and more startup to come on surface and receive the funding, trend indicated 80 times more investments are being done. The fact that ten out of thirty-five startups that were funded last year are based in offering SaaS/PaaS in the “cloud” is also remarkable. Concerning the quantitative analysis, there are indications that the majority of startup companies are using or are likely to use cloud technologies in the future. Entrepreneurs are aware of the potential benefits and challenges of the cloud. 

Cloud computing can also facilitates lean startup method. According to the lean startup method, one of its five principles is the build-measure-learn loop where you “turn ideas into products, measure how customers respond, and then learn whether to pivot or persevere” (Figure 1). But here is challenge of optimization i.e., how to reduce the time in learn loop and focus more on successful innovation. The role cloud computing plays is a major one, which is to facilitate companies to iterate through this loop in order to loop quicker, accelerate experimental cycle and infer by the data what people do with your product.

 The broad spectrum that cloud technologies offer, gives to entrepreneurs the opportunity to align their models according to customer’s needs.


\section*{Cloud Technology on Entrepreneurs}

Cloud computing could be the best the friends with the entrepreneur who wants to start venture. To begin with, the financial part, which is one the most problematic factors for doing business in Greece, cloud technologies helps by cutting some percentage of cost. Since the model of cloud computing is commission based, it’s basically free of cost. According to Blank (2012), a startup is “a temporary organization in search of a scalable, repeatable, profitable business model”. In today’s era of technology a greatest asset for any startup could be IT resources. However consumer doesn’t need for some extra provision, in case the computing power increases. Cloud computing is also very user friendly as it gives a very good grip and control over scaling, memory management. It gives the opportunity of accessing economies of scale that only the larger firms were able to take advantage of. 

However, the benefits of cloud computing are not limited to cost reduction. The value of cloud computing is more than reducing IT costs. The main advantage of cloud technology is the broad range of amenities it provides such as the management of infrastructure,   services, and the process which ultimately leads to significant innovation. Despite cloud computing is often seen as a method for cutting expenses, a larger opportunity is at stake. We are stepping into era where the driver of business agility is based in IT computing and resources. Mobility may be considered as a characteristic of an agile company. Analogically, the space is bend using the cloud computing, because it lets people collaborate with each other wherever they are in the world and lets them work on their mission to complete the project.


\section*{Effect On Greek Entrepreneurship}

We have serious indications that loud computing has the potential to affect Greek entrepreneurship and startup companies. Due to economy of Greece the startup economy is going through a series of positive change which will change the face of startup in Greece and set a benchmark. Since the cost reduction is the major focus of the companies the cloud computing is the perfect fit for their need. Cloud computing not only just reduces the cost, but the IT computing it offers and flexibility over those resources help companies collaborate and work efficiently thereby accelerating the rate of innovation.

Cloud computing has inevitably changed many aspects of how technology-based companies are formed and built but also the financing process. The cloud technology promotes the researcher mindset in entrepreneur, by letting them easily build infrastructure and test their build in real time. Concerning the technical side of the starting up process, it is easier and cheaper than ever before. Prototyping has become much cheaper, thanks to cloud computing, which help entrepreneurs to get better feedbacks and chance to improvise upon. This means market validation is quicker and efficient thereby leading to entrepreneur showing results to investors faster and thereby getting funding faster, ultimately increasing the startup economy.




\section*{Conclusion}

Cloud computing has tremendous affect on Greek startup economy, the signs are very positive which and this data could be scaled up and be interpolated in startup economy of world. To exploit the full potential of cloud computing we need to adopt it as fast as possible thereby compelling government and IT companies to set some bar over the use. Several actions should be taken from government, IT industry, customers, cloud providers and individuals:
\begin{itemize}

\item “Stakeholders” must be made aware of potential risks and challenges regarding privacy issue of the consumer of cloud computing 
\item“Stakeholders” must be educated benefits about cloud computing so that they could easily avail it’s benefits. Also made aware of the technical part of cloud computing.

\end{itemize}

\section*{References}

\begin{enumerate}

\item Padnos, C. (2012). How Cloud Computing Changes Startup Investing. Retrieved April 25,2014,from  http://sandhill.com/article/how-cloud-computing-changes-start-up-investing/

\item Pogkas, D. (2013). No Title. Retrieved April 05, 2014, from http://www.emea.gr/greek-startups-funding2013

\item Radack, S. (2012). Cloud Computing: A review of features, benefits, and risks, and recommendations for secure, efficient implementations, (June). 

\item Pieterson, M. N. B. (2009). Benefits of IT (Information Technology) in Modern Day Business. Retrieved March 19, 2014, from http://www.modernghana.com/news2/242392/1/benefits-of-itinformation-technology-in-modern-da.html 

\item 5.	Smith, J. K., Smith, R. L., & Bliss, R. T. (2011). Entrepreneurial Finance Strategy, Valuation, and Deal Structure. Spinola, M. (2009). An Essential Guide to Possibilities and Risks of Cloud Computing.

\end{enumerate}



\end{document}
